---
title: "Initial EDA"
author: "Tim Hogan"
date: "Today"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Haley: Data Summary

```{r, include=FALSE}
library(tidyverse)
library(magrittr)
library(esquisse)
library(stringr)
library(gridExtra)
library(kableExtra)
```

```{r}
Lowelldata <- read.csv("UNH Export for Haley Lowell 55932 - UNH Export for Haley Lowell 55932.csv")
```

```{r}
names <- Lowelldata[8,]

Lowell.df <- Lowelldata[9:nrow(Lowelldata),]

colnames(Lowell.df) <- c(t(names))

Lowell.df %<>% separate(Timestamp, into = c("Date","TimeStamp","AM/PM"), sep = " ")
```

```{r, echo=FALSE}
Lowell.df$Velocity <- type.convert(Lowell.df$Velocity)

Lowell.df$Odometer <- type.convert(Lowell.df$Odometer)

Lowell.df$Seconds <- type.convert(Lowell.df$Seconds)

Lowell.df$'Player Load' <- type.convert(Lowell.df$'Player Load')

Lowvel <- cbind(t(range(Lowell.df$Velocity)),mean(Lowell.df$Velocity))
Lowodo <- cbind( t(range(Lowell.df$Odometer)),mean(Lowell.df$Odometer))
Lowsec <- cbind( t(range(Lowell.df$Seconds)),mean(Lowell.df$Seconds))
Lowloa <- cbind(t(range(Lowell.df$'Player Load')),mean(Lowell.df$'Player Load'))

Lowtable <- rbind(Lowvel,Lowodo,Lowsec,Lowloa)

Lowtable <- round(Lowtable, digits =2 )

colnames <- c("Velocity","Odometer","Seconds","Player Load")

Lowtable <- cbind(colnames, Lowtable)

kable(Lowtable, digits=1, booktabs=TRUE, col.names = c("", "Minimum","Maximum","Mean")) %>%
  kable_styling(latex_options = "striped")

```

## Haley's Data

```{r, echo = FALSE}
low1 <- ggplot(Lowell.df) +
  aes(x = `Heart Rate`) +
  geom_bar(fill = "#0c4c8a") +
  labs(y = "Occurrences", title = "Haley's Heart Rates") +
  theme_minimal()

low2 <- ggplot(Lowell.df) +
  aes(x = Velocity) +
  geom_histogram(bins = 30L, fill = "#0c4c8a") +
  labs(x = "Velocity", y = "Frequency", title = " Haley's Velocities") +
  theme_minimal()

low3 <- ggplot(Lowell.df) +
  aes(x = Odometer) +
  geom_histogram(bins = 30L, fill = "#0c4c8a") +
  labs(x = "Distance Traveled", y = "Frequency", title = "Haley's Odometer") +
  theme_minimal()

low4 <- ggplot(Lowell.df) +
  aes(x = `Player Load`) +
  geom_histogram(bins = 30L, fill = "#0c4c8a") +
  labs(y = "Count", title = "Haley's Player Load") +
  theme_minimal()

grid.arrange(low1,low2,low3,low4,ncol=2,nrow=2)

```

## Haley's Player Load

```{r,echo=FALSE}
plotHaley <- ggplot(Lowell.df) +
  aes(x = Seconds, y = `Player Load`, colour = Odometer) +
  geom_point(size = 1L) +
  scale_color_viridis_c(option = "plasma") +
  labs(x = "Time (seconds)", y = "Player Load", title = "Player Load with Time", subtitle = "Player = Haley", color = "Odometer") +
  theme_minimal()
plotHaley
```

## Haley's Velocity

```{r,echo=FALSE}
HaleyVelo <- ggplot(Lowell.df) +
  aes(x = Seconds, y = `Velocity`) +
  geom_point(size = 1L, colour = "#0c4c8a") +
  labs(x = "Time (seconds)", y = "Velocity", title = "Velocity with Time", subtitle = "Player = Haley") +
  theme_minimal()
HaleyVelo
```

## Summary for Liz's Data

```{r,echo=FALSE}
Lizdata <- read.csv("UNH Export for Elizabeth Ryan 68501exp.csv")

names <- Lizdata[8,]

Liz.df <- Lizdata[9:nrow(Lizdata),]

colnames(Liz.df) <- c(t(names))

Liz.df %<>% separate(Timestamp, into = c("Date","TimeStamp","AM/PM"), sep = " ")

Liz.df$Velocity <- type.convert(Liz.df$Velocity)

Liz.df$Odometer <- type.convert(Liz.df$Odometer)

Liz.df$Seconds <- type.convert(Liz.df$Seconds)

Liz.df$Latitude <- type.convert(Liz.df$Latitude)

Liz.df$Longitude <- type.convert(Liz.df$Longitude)

Liz.df$'Player Load' <- type.convert(Liz.df$'Player Load')
```

```{r,echo=FALSE}
Lizvel <- cbind(t(range(Liz.df$Velocity)),mean(Liz.df$Velocity))
Lizodo <- cbind( t(range(Liz.df$Odometer)),mean(Liz.df$Odometer))
Lizsec <- cbind( t(range(Liz.df$Seconds)),mean(Liz.df$Seconds))
Lizloa <- cbind(t(range(Liz.df$'Player Load')),mean(Liz.df$'Player Load'))

Liztable <- rbind(Lizvel,Lizodo,Lizsec,Lizloa)

Liztable <- round(Liztable, digits =2 )

colnames <- c("Velocity","Odometer","Seconds","Player Load")

Liztable <- cbind(colnames, Liztable)

kable(Liztable, digits=1, booktabs=TRUE, col.names = c("", "Minimum","Maximum","Mean")) %>%
  kable_styling(latex_options = "striped")
```


## Liz Summary: Histograms
```{r,echo=FALSE}
liz1 <- ggplot(Liz.df) +
  aes(x = `Heart Rate`) +
  geom_bar(fill = "#0c4c8a") +
  labs(y = "Occurrences", title = "Liz's Heart Rate") +
  theme_minimal()

liz2 <- ggplot(Liz.df) +
  aes(x = Velocity) +
  geom_histogram(bins = 30L, fill = "#0c4c8a") +
  labs(x = "Velocity", y = "Frequency", title = "Liz's Velocities") +
  theme_minimal()

liz3 <- ggplot(Liz.df) +
  aes(x = Odometer) +
  geom_histogram(bins = 30L, fill = "#0c4c8a") +
  labs(x = "Distance Traveled", y = "Frequency", title = "Liz's Odometer") +
  theme_minimal()

liz4 <- ggplot(Liz.df) +
  aes(x = `Player Load`) +
  geom_histogram(bins = 30L, fill = "#0c4c8a") +
  labs(y = "Count", title = "Liz's Player Load") +
  theme_minimal()
grid.arrange(liz1,liz2,liz3,liz4,nrow=2,ncol=2)
```

## Liz: Player Load
```{r, echo=FALSE}
plotLiz <- ggplot(Liz.df) +
  aes(x = Seconds, y = `Player Load`, colour = Odometer) +
  geom_point(size = 1L) +
  scale_color_viridis_c(option = "plasma") +
  labs(x = "Time (seconds)", y = "Player Load", title = "Player Load with Time", subtitle = "Player = Liz", color = "Odometer") +
  theme_minimal()
plotLiz
```

## Liz Velocity

```{r,echo=FALSE}
LizVelo <- ggplot(Liz.df) +
  aes(x = Seconds, y = `Velocity`) +
  geom_point(size = 1L, colour = "#0c4c8a") +
  labs(x = "Time (seconds)", y = "Velocity", title = "Velocity with Time", subtitle = "Player = Haley") +
  theme_minimal()
LizVelo
```

## Comparing Liz and Haley

```{r, echo=FALSE}
grid.arrange(plotLiz,plotHaley,nrow=2)
```

## Liz's Odometer vs Player Load

```{r,echo=FALSE}
line1 <- ggplot(Liz.df) +
  aes(x = Odometer, y = `Player Load`) +
  geom_point(size = 1L, colour = "#0c4c8a") +
  labs(x = "Distance Travelled", y = "Player Load", title = "Odometer vs Player Load", subtitle = "Player = Liz") +
  theme_minimal()

line2 <- ggplot(Lowell.df) +
  aes(x = Odometer, y = `Player Load`) +
  geom_point(size = 1L, colour = "#0c4c8a") +
  labs(x = "Distance Travelled", y = "Player Load", title = "Odometer vs Player Load", subtitle = "Player = Haley") +
  theme_minimal()
grid.arrange(line1,line2,ncol=2)
```

## Liz's Location

```{r,echo=FALSE}
ggplot(Liz.df) +
  aes(x = Latitude, y = Longitude) +
  geom_point(size = 0.3, colour = "#0c4c8a") +
  labs(title = "Lat vs Long", subtitle = "Player = Liz") +
  theme_minimal()
```

## Questions

* What should we do about acceleration?
    + Is there a cutoff where we can make it 0?
    + How should we set a cutoff?

* How should we interpret latitude and longitude?

* How can we codify players and games?